---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BCyto

<!-- badges: start -->
<!-- badges: end -->

**BCyto** is is an open-source project that provides an user-friendly, high-performance user interface for Flow Cytometry analysis.

## Installation

**BCyto** can be installed by first installing R and typing the following commands in R console:

``` r
#to allow installation of GitHub packages
install.packages("devtools")
#to enable donwload of BioConductor dependencies
install.packages("BiocManager")
#BCyto can then be installed
devtools::install_github("BonilhaCaio/BCyto")
```

## Usage

**BCyto** Shiny-based user interface with all its tools is generated through the package's single function:

``` r
BCyto::runBCyto()
```

## Credits and citation

A publication where the package dependencies and imports will be appropriately credited is on the way. Meanwhile, you can cite **BCyto** as follows:

```{r, eval = TRUE}
citation("BCyto")
```
